\hypertarget{changelog}{%
\section{Changelog}\label{changelog}}

The syllabus is a live document which is regularly updated. This
syllabus and schedule are subject to change in the event of extenuating
circumstances. If you are absent from class, it is your responsibility
to check on all announcements made while you were absent.

Changes and corrections are listed in the changelog below and will be
announced on Canvas.

\begin{itemize}
\tightlist
\item
  2019-01-15: Syllabus published on Canvas
\item
  2019-01-22: Added SI information. Updated class schedule
\item
  2019-01-27: Fixed URL to class schedule and added link to LTA request
  form
\item
  2019-03-07: Updated LTA scheduling, office hours, and appointments
\end{itemize}

\newpage

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

Welcome to the second semester of course in organic chemistry (CHEM
128B)!

This course is further exploration of one of the richest and most
beautiful areas of modern chemistry: \emph{chemistry of carbon-basaed
compounds}. In CHEM 128B, we will examine topics and concepts that are
essential for understanding modern biochemistry, medicine, and the
chemical reactions related to life.

\textbf{Important note about grading:} This course uses a different
grading method to one that you might be used to. The details are
explained in sections below. \emph{Read the syllabus carefully.} It is
nearly 5,000 words for a reason. Almost all questions about the course
that you might ask can be answered by referencing the syllabus. If you
are uncertain that you understand all rules and regulations, please
contact me.

\begin{itemize}
\tightlist
\item
  \textbf{Course name and number}: CHEM 128B (75850 05-LEC)
\item
  \textbf{Units}: 3
\item
  \textbf{Pre-requisite}: Passed CHEM 128A with grade ``C'' or better.
\item
  \textbf{Meetings}: MWF 8:00--8:50 am in Science 2 Room 108
\item
  \textbf{Class schedule}: \url{https://chem128b.page.link/schedule}
  (Week = Sunday 12:00 am until Saturday 11:59 pm)
\item
  \textbf{Instructor}: Hubert Muchalski, Ph.D., Assistant Professor of
  Chemistry
\item
  \textbf{Instructor office}: Science 1 room 352
\item
  \textbf{Office Phone}: (559) 278-2711
\item
  \textbf{Email}: \url{hmuchalski@csufresno.edu} or
  \url{hmuchalski@mail.fresnostate.edu} (they go to the same inbox).
  Please note that I typically check email between 11 am and 5 pm,
  Monday thru Friday. Usually, my response time is \emph{within 6 hours
  of reading the message}. We also have online course tools where you
  can ask questions to the entire class at any time, making it more
  likely to get a quick response.
\end{itemize}

\hypertarget{office-hours-and-instructor-availability}{%
\subsection{Office hours and instructor
availability}\label{office-hours-and-instructor-availability}}

I will be available for in-office consultations Fridays 10:00--11:30 am.
Walk-in visits are welcome but students with appointments get priority.
Consultation appointments can be made on Canvas (``Find Appointments''
under Calendar). If Friday doesn't fit your schedule, please send email
me and suggest 2-3 times and we will schedule a meeting.

\hypertarget{course-materials-and-technology}{%
\subsection{Course materials and
technology}\label{course-materials-and-technology}}

\begin{itemize}
\tightlist
\item
  \textbf{Textbook:} ``Organic Chemistry, 3e'' by David Klein published
  by Wiley. This course will use the 3rd edition. Previous editions will
  also be sufficient to learn the material but page numbers as well as
  problems will be different. If you own license to e-text of the
  textbook you can access it by going to
  \url{https://online.vitalsource.com/\#/books/9781119351603}
\item
  \textbf{Solutions Manual:} Student Study Guide and Solutions Manual by
  David Klein. The solutions manual is included in the electronic
  version of the textbook.
\item
  \textbf{WileyPLUS:} You can self-enroll by clicking the following URL:
  \url{http://www.wileyplus.com/class/683136}. \textbf{IMPORTANT}:
  WileyPLUS version is tied to the edition of the textbook. Make sure
  that your access code is for the 3rd edition.
\item
  \textbf{Student response system:} Each student is required to have
  their own \texttt{i\textgreater{}clicker2} remote or access to REEF
  polling mobile app on a mobile device. You can borrow remote from a
  friend as long as they are not in my section. The officially supported
  model is \texttt{i\textgreater{}clicker2} (available at the
  Bookstore). The \texttt{i\textgreater{}clicker} and
  \texttt{i\textgreater{}clicker+} models are not compatible.
\item
  \textbf{Canvas:} The central repository for all course materials and
  information is our Canvas site, accessible through
  \url{https://fresnostate.instructure.com/}. Canvas will house your
  grades (except online homework, which is kept on the WileyPLUS site);
  links to handouts, videos, and other materials; and other course
  tools. We will often use other tools such as Google Drive, but these
  are all linked to Canvas, so keeping track of multiple websites is not
  necessary.
\end{itemize}

\hypertarget{course-goals-and-student-learning-outcomes}{%
\subsection{Course goals and student learning
outcomes}\label{course-goals-and-student-learning-outcomes}}

CHEM 128B is the second part of a two-semester sequence in organic
chemistry, the chemistry of carbon-based compounds. Topics in this
course will be focused on the principles of bonding, structure,
reactivity, and synthesis of organic materials. Also, a significant
portion of this course will address the analytical techniques routinely
used by organic chemists in their research. I hope that as you examine
the topics and concepts covered in the course, you will realize that
organic chemistry is central to understanding multiple other
disciplines. Lectures and problems will often feature organic compounds
and reactions in the context of biology, pharmacy, medicine, materials,
and energy science.

Students will be expected to demonstrate competence in self-regulated
learining of new technical material, managing time and tasks, and
educational interactions with peers.

Students will develop competence in broad areas of organic chemistry and
demonstrate the application of these concepts and theories. Students
will apply their understanding of terminology, concepts, theories, and
skills to solve problems by defining problems and research questions
clearly, formulating testable hypotheses, designing and conducting
experimental tests of hypotheses, analyzing and interpreting data, and
drawing appropriate conclusions within professional ethical guidelines.
Specifically, students who successfully complete this course you will be
able to:

\begin{itemize}
\tightlist
\item
  use common drawing and naming conventions to communicate the structure
  and properties of organic molecules;
\item
  analyze chemical structures and reactions to make and defend
  predictions about chemical transformations;
\item
  use curved arrow notation to depict mechanisms of chemical reactions;
\item
  design a synthesis of an organic molecule;
\item
  reflect on how organic chemistry relates to materials, life sciences,
  and medicine; and
\end{itemize}

\hypertarget{how-to-achieve-course-goals}{%
\section{How to achieve course
goals}\label{how-to-achieve-course-goals}}

The work you will be asked to do in- and outside of class is designed to
promote learning of the concepts of the course Learning happens by
doing, not just by listening. So to reach the learning goals in this
course, you'll be doing a wide variety of \emph{learning activities}
both in and outside of class.

\hypertarget{in-class-requirements}{%
\subsection{In-class requirements}\label{in-class-requirements}}

Three 50-minute meetings per week (MWF) where we review, discuss, and
practice concepts from the course. You'll be working with your
classmates to make sense of concepts and work on creative applications
of those basics through group problem-solving sessions, discussions
driven by interactive polling activities, and more. (3 hours per week).

\hypertarget{out-of-class-requirements}{%
\subsection{Out-of-class requirements}\label{out-of-class-requirements}}

Prior to the class meeting, students are required to work actively to
get their first contact with new concepts by reading the textbook,
watching videos, and completing the ORION baseline diagnostic activity.

After class meeting, students should regularly study the material by
doing practice problems, completing online homework, and other
assignments (approximately 9 hours per week).

\hypertarget{supplemental-instruction}{%
\subsection{Supplemental Instruction}\label{supplemental-instruction}}

Supplemental Instruction (SI) is provided for all students who want to
improve their understanding of the material taught in this course. SI
sessions for this course are led by a SI leader who has already
completed the course material and has been trained to facilitate group
sessions where students can meet to compare class notes, review and
discussimportant concepts, develop strategies for studying, and prepare
for exams. The SI leader attends this class and communicates regularly
with the instructor to ensure that accurate information is given.

The SI Leader for this course is Bhvandip (Bob) Bajwa
(\href{mailto:bsbajwa@mail.fresnostate.edu}{\nolinkurl{bsbajwa@mail.fresnostate.edu}}).

Sessions:

\begin{itemize}
\tightlist
\item
  Wednesdays 3:30PM-5:00PM in Grosse Industrial Tech (IT) room 117
\item
  Fridays 9:00AM-10:30AM in University Center 202
\end{itemize}

Office Hours:

\begin{itemize}
\tightlist
\item
  Mondays 11:00AM-12:30PM in the Learning Center
\item
  Thursdays 11:00AM-12:30PM in the Learning Center
\end{itemize}

\emph{Attendance at SI sessions is free and voluntary for any student
enrolled in this course.} Students may attend as many times as they
choose. Learn more by watching this video:
\url{http://youtu.be/yTLGu5TLOUI}

\hypertarget{types-of-graded-work}{%
\section{Types of graded work}\label{types-of-graded-work}}

There are five primary kinds of assignments and tests that you will
encounter in this course:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  WileyPLUS ORION online assignments that will assess how much you
  learned by yourself by reading the textbook, watching online videos,
  etc.\\
\item
  WileyPLUS ``Mastery'' online homework to build expertise in newly
  introduced concepts.
\item
  WileyPLUS ``level 1'' assignments that test fundamentals of
  spectroscopy and synthesis.
\item
  Learning Target Assessments (LTAs). Short quizzes assessing learning
  within one unit of material, a Learning Target.
\item
  Take-home assignments to assess learning objectives that involve
  higher level concepts and cognitive processes.
\item
  Final Exam.
\end{enumerate}

A complete listing of the criteria used to assign grades to these items
is found in \protect\hyperlink{rubrics}{Appendix A, ``Grading
Standards''}.

\hypertarget{pre-class-assignments-wileyplus}{%
\subsection{Pre-class assignments
(WileyPLUS)}\label{pre-class-assignments-wileyplus}}

This class is designed according to a model in which pre-class readings,
videos, and Skill Builder problems provide you with a structured
introduction to the basic ideas of new material so that we can review,
discuss, and practice concepts during in-class meetings. Completing the
pre-class ORION diagnostic assignment serves two roles. First, it gives
you an idea about the level of mastery you achieved from reading the
textbook, watching online videos, etc. Second, it guides my decisions
about what activities to plan and what concepts to focus on in the
upcoming class meetings.

Pre-class assignments are graded either \emph{Satisfactory} or
\emph{Unsatisfactory} on the basis of completeness and effort (not
correctness). Deadlines for submitting pre-class assignments are listed
on class schedule and on Canvas.

\hypertarget{online-homework-wileyplus}{%
\subsection{Online homework
(WileyPLUS)}\label{online-homework-wileyplus}}

This assignment requires that you show that you mastered the material.
You can attempt each question only once, however if you do not get a
percentage correct to show mastery, you can reset the assignment and try
again. Resetting the assignment will generate a new set of questions for
you to attempt. Your best attempt at this assignment will be your final
recorded score. Resetting the assignment will not change the difficulty
level of the questions. Details and deadlines for submitting online
homework will be listed on WileyPLUS.

\hypertarget{learning-target-assessments-ltas}{%
\subsection{Learning target assessments
(LTAs)}\label{learning-target-assessments-ltas}}

The content and the skills you will learn in the course are divided into
multiple \protect\hyperlink{LT}{Learning Targets} (LTs). There is
approximately one learning target for each chapter of the textbook that
we will cover this semester.

Throughout the semester, you will be asked to provide evidence that you
mastered the skills and concepts that by completing short quizzes, each
addressing a single Learning Target. The quizzes, called Learning Target
Assessments, or LTAs, are graded either \emph{satisfactory} or
\emph{progressing}. What constitutes \emph{satisfactory} or
\emph{progressing} work will be spelled out explicitly for each Learning
Target and made known to you in advance but typically it means answering
correctly \textgreater75\% of queststions. (A sample LTA for each
chapter will be posted on Canvas.)

Each attempt requires a token (\protect\hyperlink{tokens}{see section
below} for more details). Students can attempt LTAs during in-class
sessions, during office hours, or by appoinment. LTAs can be attempted
multiple times. There are mechanisms set in place to encourage/force you
to maintain reasonable progress on your portfolio throughout the
semester and not to procrastinate, and also to keep the grading workload
small enough that I can get feedback to you quickly. Check section on
\protect\hyperlink{revisions}{Reasessment} below for details.

\hypertarget{take-home-assignments}{%
\subsection{Take-home assignments}\label{take-home-assignments}}

Students who aspire to receive the highest grade in this course and/or
consider using me as a reference for their graduate/professional school
applications will be asked to earn \emph{satisfactory} grade on
additional take-home assignments on spectroscopy, synthesis, and other
special topics.

\hypertarget{final-examination}{%
\subsection{Final examination}\label{final-examination}}

Final exam will be on \textbf{Wednesday, May 15th, 08:45--10:45 AM}.
Final exam is composed of 70 multiple choice questions designed by
experts from the American Chemical Society.

\hypertarget{participation}{%
\subsection{Participation}\label{participation}}

You will also have opportunity to earn \emph{participation credits
(PC)}. A participation credit will be awarded for participation in
clicker questions or asking an insightful question in class or during
office hours. Some additional participation credit opportunities may be
announced in advance.

Research shows that student response systems (clickers) help students
learn more and do better in the course. I have successfully used the
student response system to gauge student learning and direct the flow of
the lecture. Student polling will be used in almost every lecture and
students must respond to at least 75\% of questions on a particular day
to earn PC for participation in the session.

\hypertarget{how-your-course-grade-is-determined}{%
\section{How your course grade is
determined}\label{how-your-course-grade-is-determined}}

CHEM 128B uses a mastery-based grading system that is designed to
provide you with control over the grading process. Your course grade in
CHEM 128B will be determined by the quantity and quality of evidence you
can provide that you have mastered the concepts of the course. At the
beginning of the semester, you will be able to decide on the target
grade you plan to earn for the course. This can be an ``A'', ``B'', or
even a ``C'', depending on your circumstance.

\textbf{You will have multiple attempts to earn a \emph{satisfactory}
grade on majority of key assignments}. The grading system in this course
allows revisions and multiple attempts to demonstrate a
\emph{satisfactory} level of learning. Grades on LTAs are not ﬁnal until
the end of the semester because quizzes can be attempted again.
\protect\hyperlink{revisions}{Quiz retake policy} is described in more
detail below (see \protect\hyperlink{course-policies}{Course Policies}
section).

\hypertarget{final-letter-grade}{%
\subsection{Final letter grade}\label{final-letter-grade}}

The grade you earn at the end of the semester is determined by refering
to table below. There are no statistical or numerical adjust (a.k.a.
grading on a curve). All items within ``grade bundle'' must be completed
to receive the letter grade. Failing grade (F) is given if not all the
requirements for a ``D'' are met.

\hypertarget{d-bundle}{%
\subsubsection{``D'' Bundle}\label{d-bundle}}

\begin{itemize}
\item
  completed ORION assignments for chapters 1-11;
\item
  completed 5 ORION pre-class assignments;
\item
  \emph{satisfactory} on 5 Chapter LTAs;
\item
  two of the following:

  \begin{itemize}
  \tightlist
  \item
    40\% on WileyPLUS Mastery homework,
  \item
    40\% of \emph{Participation Credits},
  \item
    40\% Proficiency on ORION;
  \end{itemize}
\item
  20\% on the final (ACS) exam;
\end{itemize}

\hypertarget{c-bundle}{%
\subsubsection{``C'' Bundle}\label{c-bundle}}

\begin{itemize}
\item
  completed ORION assignments for chapters 1-11;
\item
  completed 6 ORION pre-class assignments;
\item
  \emph{satisfactory} on 6 Chapter LTAs;
\item
  \emph{satisfactory} on spectroscopy (level 1);
\item
  \emph{satisfactory} on synthesis (level 1);
\item
  two of the following:

  \begin{itemize}
  \tightlist
  \item
    50\% on WileyPLUS Mastery homework,
  \item
    50\% of \emph{Participation Credits},
  \item
    50\% Proficiency on ORION;
  \end{itemize}
\item
  30\% on the final (ACS) exam.
\end{itemize}

\hypertarget{b-bundle}{%
\subsubsection{``B'' Bundle}\label{b-bundle}}

\begin{itemize}
\item
  completed ORION assignments for chapters 1-11;
\item
  completed 7 ORION pre-class assignments;
\item
  \emph{satisfactory} on 7 Chapter LTAs;
\item
  two of the following:

  \begin{itemize}
  \tightlist
  \item
    \emph{satisfactory} on spectroscopy (level 2);
  \item
    \emph{satisfactory} on synthesis (level 2);
  \item
    \emph{satisfactory} on special topic essay;
  \item
    50\% on final exam;
  \end{itemize}
\item
  two of the following:

  \begin{itemize}
  \tightlist
  \item
    60\% on WileyPLUS Mastery homework,
  \item
    60\% of \emph{Participation Credits},
  \item
    60\% Proficiency on ORION;
  \end{itemize}
\item
  40\% on the final (ACS) exam.
\end{itemize}

\hypertarget{a-bundle}{%
\subsubsection{``A'' Bundle}\label{a-bundle}}

\begin{itemize}
\item
  completed ORION assignments for chapters 1-11
\item
  completed 8 ORION pre-class assignments
\item
  \emph{satisfactory} on 8 Chapter LTAs
\item
  three of the following:

  \begin{itemize}
  \tightlist
  \item
    \emph{satisfactory} on spectroscopy (level 3);
  \item
    \emph{satisfactory} on synthesis (level 3);
  \item
    \emph{satisfactory} on special topic essay;
  \item
    60\% on final exam
  \end{itemize}
\item
  two of the following:

  \begin{itemize}
  \tightlist
  \item
    70\% on WileyPLUS Mastery homework,
  \item
    70\% of \emph{Participation Credits},
  \item
    70\% Proficiency on ORION
  \end{itemize}
\item
  50\% on the final (ACS) exam
\end{itemize}

\hypertarget{revisions}{%
\subsection{Reassessment}\label{revisions}}

The grading system in our course insists that you show consistent
excellence in all assignments in the course---outstanding work on
homework, for example, does not ``bring up'' poor work on LTAs. This can
be challenging, but the course also provides a robust system of revision
and reassessment for most graded tasks, so that if you aren't happy with
a grade on an assignment, you'll have multiple chances to try again or
fix any mistakes.

Scores for WileyPLUS ``Mastery'' homework are final. If you do not get a
percentage correct to show mastery (\textgreater75\%), you can reset the
assignment and try again until the deadline.

Students can request reassessment for any unsuccessful LTAs. Each
additional attempt will cover the same material and have similar
problems but will not be identical to past quizzes. Students can attempt
up to three LTAs during a reassessment session or up to two LTAs during
a single office hour visit. The 20-minute of LTA is firm and no extra
time will be allowed. To request a (re)assessment, student must reserve
an appointment on Canvas (look for ``Find Appointments'' feature in
Calendar).

I found that students tend to defer LTAs until it's too late. Thus, if
an attempt at passing a chapter LTA occurs later then 3 weeks after
covering it in class (first attempt) or 3 weeks after previous
unsuccesful attempt, it will cost two
\protect\hyperlink{tokens}{tokens}.

If you receive either a \emph{Progressing} or \emph{Incomplete} mark,
you will receive feedback on your work, and you can use the feedback to
make corrections and then resubmit your work for regrading. You may
submit up to one revision per week.

\hypertarget{tokens}{%
\subsection{Tokens}\label{tokens}}

Tokens are a ``currency'' in the course that you use to purchase LTA
attempts, assignment regrades, and exceptions to some course rules. Each
student begins the course with 20 tokens, and tokens can purchase any of
the following:

\begin{itemize}
\tightlist
\item
  one token buys one attempt at passing one LTA;
\item
  one token buys 24-hour deadline extension for online ``Mastery''
  homework;
\item
  two tokens buy one attempt at one LTA beyond the three week window;
\item
  two tokens buy one participation credit; and
\item
  three tokens buy ORION proficiency meter reset.
\end{itemize}

\hypertarget{what-are-my-expectations}{%
\section{What are my expectations?}\label{what-are-my-expectations}}

\textbf{I want you to be successful in this course.} I will do my utmost
to help you do this, by creating and maintaining a learning environment
based on challenge and support and giving my highest professional
commitment to your success and well-being. But, \textbf{I cannot achieve
success for you}. Success in college courses comes from cooperation with
instructors, interaction with your classmates, and diligent effort
throughout the semester. I like to compare successful classroom
interactions to interactions between players and coaches on a sports
team. Players do the work and coaches make sure players do the work that
helps players succeed.

To be successful in the course, you need to make sure you are always
giving an effort to do the following:

\begin{itemize}
\tightlist
\item
  Prepare for the class through the pre-class learning exercises (Skill
  Builder).
\item
  Attend all class meetings and participate in class activities.
\item
  Be proactive in completing course work and avoid procrastination in
  all things.
\item
  Maintain awareness of course announcements and calendar events, by
  regularly checking email, and the course calendar.
\item
  Take initiative to seek out help when you are stuck or have a question
  by using office visits, SI, study groups, and whatever else works for
  you.
\item
  Maintain a positive attitude about the class and what you are
  learning.
\end{itemize}

There are many strategies to study Organic Chemistry. The hardest and
one I don't recommend is rote memorization. There will be a lot of new
words, definitions, names, and structures that you will have to commit
to memory. Memorizing \emph{everything}, however, is nearly impossible
because the amount of material that is covered increases dramatically as
the semester progresses. Understanding of the trends, principles,
connections, and logic of chemical transformation will give you better
chances of success.

\hypertarget{expectations-for-professor}{%
\subsection{Expectations for
professor}\label{expectations-for-professor}}

My primary responsibility is to create a learning environment where it's
safe to take risks and make mistakes, without shaming or judgment, and
to give you feedback and guidance as you grow in your understanding of
the subject. As my students, you have a right to expect from me:

\begin{itemize}
\tightlist
\item
  carefully designed and executed learning activities both in and out of
  class;
\item
  informative feedback on, and timely return of all graded work (I
  strive to return all graded work within one week of your turning it
  in);
\item
  timely responses to all communications; and
\item
  respectful, professional treatment in all personal interactions.
\end{itemize}

If you perceive that I am falling short in any of these expectations,
you have the right and responsibility to give constructive feedback that
helps me improve. I will consider all reasonable suggestions in the
course regarding my instruction or the course design.

\hypertarget{supplemental-instruction-1}{%
\subsection{Supplemental Instruction}\label{supplemental-instruction-1}}

Supplemental Instruction (SI) is provided for all students who want to
improve their understanding of the material taught in this course. SI
sessions are led by a student who has already mastered the course
material and has been trained to facilitate group sessions where
students can meet to compare class notes, review and discussimportant
concepts, develop strategies for studying, and prepare for exams. The SI
leader attends this class and communicates regularly with the instructor
to ensure that accurate information is given. Attendance at SI sessions
is free and voluntary for any student enrolled in this course. Students
may attend as many times as they choose. A session schedule will be
announced in the first few weeks of class. Learn more by watching this
video: \url{http://youtu.be/yTLGu5TLOUI}

\hypertarget{course-policies}{%
\section{Course policies}\label{course-policies}}

\hypertarget{technology-issues-when-submitting-work}{%
\subsection{Technology issues when submitting
work}\label{technology-issues-when-submitting-work}}

WileyPLUS and ORION assignments are submitted electronically. It is the
student's responsibility to make sure these items are submitted on time,
through any means necessary, even if technology issues arise. If a tech
issue arises that prevents your being able to submit work on time, it is
your responsibility to find another way to get it to me (for example,
via an email attachment). Technology issues that are avoidable or
resolved with a simple work-around will not be considered valid grounds
for a deadline extension. For example, if you are trying to upload a Lab
to Canvas and Canvas won't accept the file, you should try again later
or send the file as an email attachment until you can upload it
successfully.

\hypertarget{recording-of-in-class-content}{%
\subsection{Recording of in-class
content}\label{recording-of-in-class-content}}

Audio and video recordings of class lectures are prohibited unless I
give you explicit permission to do it. Students with an official letter
from the Services for Students with Disabilities office may record the
class if SSD has approved that service.

\hypertarget{academic-dishonesty}{%
\subsection{Academic Dishonesty}\label{academic-dishonesty}}

Your work on Learning Target Assessments must be done individually, and
all collaboration is prohibited.

For take-home assignments you are allowed and encouraged to work with
others. However, the final product that you submit for feedback must be
the result of your own efforts. Therefore, you may share ideas and
strategies with others, but collaboration on the actual finished product
you submit is not allowed. Your work is expected to be the product of
your own thinking, written and explained in your own words with no parts
of the work copied from external sources such as books or websites, and
done clearly enough in your own mind that you could explain the work
from start to finish if asked. Specifically, this excludes:

\begin{itemize}
\tightlist
\item
  copying work from another student;
\item
  copying work from a website;
\item
  paraphrasing work done by another student or from print or internet
  resources---i.e.~putting it in your own words---without coming up with
  the main ideas and strategies yourself; and
\item
  \emph{allowing or enabling} another student to copy or paraphrase work
  that you did, even if you did the original work yourself.
\end{itemize}

Violation of this policy is considered ``academic dishonesty'' and
carries with it strong punitive measures mandated by Fresno State,
including possible automatic failure of the course or suspension from
the university. For details, please see APM 235 by going to
\url{http://www.fresnostate.edu/aps/documents/apm/235.pdf}.

You may feel tempted to academic dishonesty at some point in the
semester. The work can be difficult, and many of you are under a lot of
stress. If you are considering academic dishonesty, please STOP, take a
breath, and remember that your classmates and I want you to succeed in
the course. You are not alone, and you have a strong network in the
class for getting help. The revision and resubmission policies mean that
it's OK to turn in work that isn't perfect. There is no need to be
academically dishonest! Just do your best on the work, and you'll have
the chance to revise it later.

\hypertarget{dropping-the-course}{%
\subsection{Dropping the course}\label{dropping-the-course}}

Students may drop classes using the on-line system through Thursday,
February. The Drop/Withdrawal Form, signed by instructor and department
chair, is needed to drop a course after that date. Withdrawals processed
before 9/20 will not show on the official transcript. Serious and
compelling drop period begins on September 21 and ends on November 20.
More details on
\href{http://fresnostate.edu/studentaffairs/are/registration/add-drop-deadlines.html}{Admissions
web pages}

A \emph{serious and compelling reason} is defined as an unexpected
condition that is not present prior to enrollment in the course that
unexpectedly arises and interferes with a student's ability to attend
class meetings and/or complete course requirements. The reason must be
acceptable to and verified by the instructor of record and the
department chair. The condition must be stated in writing on the
appropriate form. The student must provide documentation that
substantiates the condition.

Failing or performing poorly in a class is not an acceptable ``serious
and compelling reason'' within the University policy, nor is
dissatisfaction with the subject matter, class or instructor.

\hypertarget{university-policies-and-disclaimers}{%
\section{University policies and
disclaimers}\label{university-policies-and-disclaimers}}

In addition to course policies, you are expected to be familiar with
Academic Regulations described in the
\href{http://www.fresnostate.edu/catalog/academic-regulations/}{University
Catalog} as well as policies listed below.

\begin{itemize}
\tightlist
\item
  Class Schedule Policies:
  \url{http://fresnostate.edu/studentaffairs/classschedule/policy/}
\item
  Copyright Policy: \url{http://libguides.csufresno.edu/copyright}
\item
  Students with Dissabilities:
  \url{http://fresnostate.edu/studentaffairs/careers/students/interests/disabilities.html}
\item
  Academic Integrity:
  \url{http://fresnostate.edu/studentaffairs/studentconduct/academic-integrity/}
\item
  Policy on Cheating and Plagiarism:
  \url{http://fresnostate.edu/studentaffairs/studentconduct/policies/cheating-plagiarism.html}
\item
  Add/Drop Course:
  \href{http://fresnostate.edu/studentaffairs/classschedule/registration/add-drop.html}{http://www.fresnostate.edu/studentaffairs/registrar/registration/add-drop-deadlines.html}
\end{itemize}

\newpage

\hypertarget{rubrics}{%
\section{Appendix A: Grading rubrics}\label{rubrics}}

\begin{itemize}
\tightlist
\item
  Pre-class ORION assignments are graded either \emph{satisfactory} (S)
  or \emph{unsatisfactory} (U) and are graded on the basis of
  completeness, effort, and timeliness.
\end{itemize}

\begin{longtable}[]{@{}ll@{}}
\toprule
\begin{minipage}[b]{0.30\columnwidth}\raggedright
Mark\strut
\end{minipage} & \begin{minipage}[b]{0.64\columnwidth}\raggedright
Description\strut
\end{minipage}\tabularnewline
\midrule
\endhead
\begin{minipage}[t]{0.30\columnwidth}\raggedright
S\strut
\end{minipage} & \begin{minipage}[t]{0.64\columnwidth}\raggedright
Completed initial diagnostic activity for the chapter. Every item on the
assignment has a response that represents a good-faith effort to answer
correctly; and the work is submitted before the deadline.\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.30\columnwidth}\raggedright
U\strut
\end{minipage} & \begin{minipage}[t]{0.64\columnwidth}\raggedright
No work submitted; or work is submitted that is late, has at least one
blank response, or at least one response that is not a serious
attempt.\strut
\end{minipage}\tabularnewline
\bottomrule
\end{longtable}

\begin{itemize}
\tightlist
\item
  WileyPLUS Mastery assignments are typically 10 questions on a
  particular topic and require that you attempt each of the questions
  and get a total percentage correct. You can attempt each question only
  once, however if you do not get a percentage correct to show mastery
  (\textgreater75\%), you can reset the assignment and try again.
  Resetting the assignment will generate a new set of questions for you
  to attempt. Your best attempt at this assignment will be your final
  recorded score. Resetting the assignment will not change the
  difficulty level of the questions. 75\% or more correct to receive 10
  points; 50\% or more correct to receive 5 points; less than 50\%
  correct to receive 0 points.
\item
  Learning Target Assessments (LTAs) are graded either Satisfactory (S)
  or Progressing (P) using criteria spelled out individually for each
  target.
\item
  Take-home assignments are graded either Satisfactory (S), Progressing
  (P), or Incomplete (I). The base criteria for all assignments are as
  follows (some may have additional criteria which will be explained
  withing the assignment):
\end{itemize}

\begin{longtable}[]{@{}ll@{}}
\toprule
\begin{minipage}[b]{0.30\columnwidth}\raggedright
Mark\strut
\end{minipage} & \begin{minipage}[b]{0.64\columnwidth}\raggedright
Description\strut
\end{minipage}\tabularnewline
\midrule
\endhead
\begin{minipage}[t]{0.30\columnwidth}\raggedright
S\strut
\end{minipage} & \begin{minipage}[t]{0.64\columnwidth}\raggedright
Understanding of the concepts is evident, although there may be a small
number of mistakes in the work that do not significantly affect the
overall reasoning. All solutions are backed up by work that is clearly
shown and easy to read.\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.30\columnwidth}\raggedright
P\strut
\end{minipage} & \begin{minipage}[t]{0.64\columnwidth}\raggedright
Partial understanding of concepts is evident, and all parts of the
solution have a good-faith attempt. But there are significant errors in
computation, logic, or writing that affect the overall reasoning. The
work should be revised.\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.30\columnwidth}\raggedright
I\strut
\end{minipage} & \begin{minipage}[t]{0.64\columnwidth}\raggedright
No work submitted or there are significant omissions in the work, such
as parts of the solution left blank intentionally or essential parts of
the reasoning behind the answers that are missing or unreadable. Not
enough information to determine if the concepts are fully
understood.\strut
\end{minipage}\tabularnewline
\bottomrule
\end{longtable}

\newpage

\hypertarget{course-calendar}{%
\section{Course calendar}\label{course-calendar}}

\hypertarget{important-dates}{%
\subsection{Important dates}\label{important-dates}}

\begin{longtable}[]{@{}llll@{}}
\toprule
\begin{minipage}[b]{0.05\columnwidth}\raggedright
Date\strut
\end{minipage} & \begin{minipage}[b]{0.03\columnwidth}\raggedright
Day\strut
\end{minipage} & \begin{minipage}[b]{0.43\columnwidth}\raggedright
Item\strut
\end{minipage} & \begin{minipage}[b]{0.38\columnwidth}\raggedright
Comment\strut
\end{minipage}\tabularnewline
\midrule
\endhead
\begin{minipage}[t]{0.05\columnwidth}\raggedright
01/15\strut
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
Tue\strut
\end{minipage} & \begin{minipage}[t]{0.43\columnwidth}\raggedright
First day of Spring Semester\strut
\end{minipage} & \begin{minipage}[t]{0.38\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.05\columnwidth}\raggedright
01/17\strut
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
Thu\strut
\end{minipage} & \begin{minipage}[t]{0.43\columnwidth}\raggedright
First day of instruction\strut
\end{minipage} & \begin{minipage}[t]{0.38\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.05\columnwidth}\raggedright
01/21\strut
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
Mon\strut
\end{minipage} & \begin{minipage}[t]{0.43\columnwidth}\raggedright
Holiday - Martin Luther King Jr.~Day\strut
\end{minipage} & \begin{minipage}[t]{0.38\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.05\columnwidth}\raggedright
02/07\strut
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
Thu\strut
\end{minipage} & \begin{minipage}[t]{0.43\columnwidth}\raggedright
Last day to drop course online via Student Center\strut
\end{minipage} & \begin{minipage}[t]{0.38\columnwidth}\raggedright
Permission not required. No {[}W{]} will show on transcript\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.05\columnwidth}\raggedright
02/13\strut
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
Wed\strut
\end{minipage} & \begin{minipage}[t]{0.43\columnwidth}\raggedright
Last day to drop course via paper form\strut
\end{minipage} & \begin{minipage}[t]{0.38\columnwidth}\raggedright
Permission required. No {[}W{]} will show on transcript.\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.05\columnwidth}\raggedright
02/18\strut
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
Mon\strut
\end{minipage} & \begin{minipage}[t]{0.43\columnwidth}\raggedright
Holiday - President's Day\strut
\end{minipage} & \begin{minipage}[t]{0.38\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.05\columnwidth}\raggedright
04/01\strut
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
Mon\strut
\end{minipage} & \begin{minipage}[t]{0.43\columnwidth}\raggedright
Holiday - Cesar Chavez Day\strut
\end{minipage} & \begin{minipage}[t]{0.38\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.05\columnwidth}\raggedright
04/15\strut
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
Mon\strut
\end{minipage} & \begin{minipage}[t]{0.43\columnwidth}\raggedright
Spring Break begins\strut
\end{minipage} & \begin{minipage}[t]{0.38\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.05\columnwidth}\raggedright
04/16\strut
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
Tue\strut
\end{minipage} & \begin{minipage}[t]{0.43\columnwidth}\raggedright
Last day to drop for serious and compelling reason (paper form)\strut
\end{minipage} & \begin{minipage}[t]{0.38\columnwidth}\raggedright
Permission required. {[}W{]} will show on transcript.\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.05\columnwidth}\raggedright
05/08\strut
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
Wed\strut
\end{minipage} & \begin{minipage}[t]{0.43\columnwidth}\raggedright
Last day of Fall instruction\strut
\end{minipage} & \begin{minipage}[t]{0.38\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.05\columnwidth}\raggedright
05/10\strut
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
Fri\strut
\end{minipage} & \begin{minipage}[t]{0.43\columnwidth}\raggedright
Last day to retake LTAs\strut
\end{minipage} & \begin{minipage}[t]{0.38\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.05\columnwidth}\raggedright
05/15\strut
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
Tue\strut
\end{minipage} & \begin{minipage}[t]{0.43\columnwidth}\raggedright
Final exam (08:45-10:45 AM)\strut
\end{minipage} & \begin{minipage}[t]{0.38\columnwidth}\raggedright
ACS exam (multiple choice)\strut
\end{minipage}\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{class-meeting-schedule}{%
\subsection{Class meeting schedule}\label{class-meeting-schedule}}

\begin{longtable}[]{@{}llllll@{}}
\toprule
\begin{minipage}[b]{0.03\columnwidth}\raggedright
W\strut
\end{minipage} & \begin{minipage}[b]{0.03\columnwidth}\raggedright
L\strut
\end{minipage} & \begin{minipage}[b]{0.06\columnwidth}\raggedright
Date\strut
\end{minipage} & \begin{minipage}[b]{0.04\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[b]{0.49\columnwidth}\raggedright
Topics of in-class meeting\strut
\end{minipage} & \begin{minipage}[b]{0.17\columnwidth}\raggedright
Reading assignment\strut
\end{minipage}\tabularnewline
\midrule
\endhead
\begin{minipage}[t]{0.03\columnwidth}\raggedright
1\strut
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
1\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright
01/18\strut
\end{minipage} & \begin{minipage}[t]{0.04\columnwidth}\raggedright
Fri\strut
\end{minipage} & \begin{minipage}[t]{0.49\columnwidth}\raggedright
Introductions\strut
\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedright
Syllabus\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.03\columnwidth}\raggedright
2\strut
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
X\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright
01/21\strut
\end{minipage} & \begin{minipage}[t]{0.04\columnwidth}\raggedright
Mon\strut
\end{minipage} & \begin{minipage}[t]{0.49\columnwidth}\raggedright
NO CLASS (MLK Day)\strut
\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.03\columnwidth}\raggedright
2\strut
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
2\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright
01/23\strut
\end{minipage} & \begin{minipage}[t]{0.04\columnwidth}\raggedright
Wed\strut
\end{minipage} & \begin{minipage}[t]{0.49\columnwidth}\raggedright
Acid--base reactions of alcohols. The Grignard reaction.\strut
\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedright
Chapter 12\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.03\columnwidth}\raggedright
2\strut
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
3\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright
01/25\strut
\end{minipage} & \begin{minipage}[t]{0.04\columnwidth}\raggedright
Fri\strut
\end{minipage} & \begin{minipage}[t]{0.49\columnwidth}\raggedright
Redox reactions that involve alcohols\strut
\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.03\columnwidth}\raggedright
3\strut
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
4\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright
01/28\strut
\end{minipage} & \begin{minipage}[t]{0.04\columnwidth}\raggedright
Mon\strut
\end{minipage} & \begin{minipage}[t]{0.49\columnwidth}\raggedright
Alcohols in organic synthesis.\strut
\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.03\columnwidth}\raggedright
3\strut
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
5\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright
01/30\strut
\end{minipage} & \begin{minipage}[t]{0.04\columnwidth}\raggedright
Wed\strut
\end{minipage} & \begin{minipage}[t]{0.49\columnwidth}\raggedright
Ring-opening reactions of epoxides\strut
\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedright
Chapter 13\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.03\columnwidth}\raggedright
3\strut
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
6\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright
02/01\strut
\end{minipage} & \begin{minipage}[t]{0.04\columnwidth}\raggedright
Fri\strut
\end{minipage} & \begin{minipage}[t]{0.49\columnwidth}\raggedright
Ethers and epoxides in organic synthesis\strut
\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.03\columnwidth}\raggedright
4\strut
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
7\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright
02/04\strut
\end{minipage} & \begin{minipage}[t]{0.04\columnwidth}\raggedright
Mon\strut
\end{minipage} & \begin{minipage}[t]{0.49\columnwidth}\raggedright
Infrared (IR) spectroscopy\strut
\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedright
Chapter 14\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.03\columnwidth}\raggedright
4\strut
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
8\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright
02/06\strut
\end{minipage} & \begin{minipage}[t]{0.04\columnwidth}\raggedright
Wed\strut
\end{minipage} & \begin{minipage}[t]{0.49\columnwidth}\raggedright
Mass spectrometry\strut
\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.03\columnwidth}\raggedright
4\strut
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
9\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright
02/08\strut
\end{minipage} & \begin{minipage}[t]{0.04\columnwidth}\raggedright
Fri\strut
\end{minipage} & \begin{minipage}[t]{0.49\columnwidth}\raggedright
NMR: Chemical shift and integration\strut
\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedright
Chapter 15\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.03\columnwidth}\raggedright
5\strut
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
10\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright
02/11\strut
\end{minipage} & \begin{minipage}[t]{0.04\columnwidth}\raggedright
Mon\strut
\end{minipage} & \begin{minipage}[t]{0.49\columnwidth}\raggedright
NMR: signal shape (multiplicity)\strut
\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.03\columnwidth}\raggedright
5\strut
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
11\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright
02/13\strut
\end{minipage} & \begin{minipage}[t]{0.04\columnwidth}\raggedright
Wed\strut
\end{minipage} & \begin{minipage}[t]{0.49\columnwidth}\raggedright
Spectroscopic analysis in practice\strut
\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.03\columnwidth}\raggedright
5\strut
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
12\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright
02/15\strut
\end{minipage} & \begin{minipage}[t]{0.04\columnwidth}\raggedright
Fri\strut
\end{minipage} & \begin{minipage}[t]{0.49\columnwidth}\raggedright
Spectroscopic analysis in practice\strut
\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.03\columnwidth}\raggedright
6\strut
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
X\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright
02/18\strut
\end{minipage} & \begin{minipage}[t]{0.04\columnwidth}\raggedright
Mon\strut
\end{minipage} & \begin{minipage}[t]{0.49\columnwidth}\raggedright
NO CLASS (President's Day)\strut
\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.03\columnwidth}\raggedright
6\strut
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
13\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright
2/20\strut
\end{minipage} & \begin{minipage}[t]{0.04\columnwidth}\raggedright
Wed\strut
\end{minipage} & \begin{minipage}[t]{0.49\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.03\columnwidth}\raggedright
6\strut
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
14\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright
2/22\strut
\end{minipage} & \begin{minipage}[t]{0.04\columnwidth}\raggedright
Fri\strut
\end{minipage} & \begin{minipage}[t]{0.49\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.03\columnwidth}\raggedright
7\strut
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
15\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright
2/25\strut
\end{minipage} & \begin{minipage}[t]{0.04\columnwidth}\raggedright
Mon\strut
\end{minipage} & \begin{minipage}[t]{0.49\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.03\columnwidth}\raggedright
7\strut
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
16\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright
2/27\strut
\end{minipage} & \begin{minipage}[t]{0.04\columnwidth}\raggedright
Wed\strut
\end{minipage} & \begin{minipage}[t]{0.49\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.03\columnwidth}\raggedright
7\strut
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
17\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright
3/1\strut
\end{minipage} & \begin{minipage}[t]{0.04\columnwidth}\raggedright
Fri\strut
\end{minipage} & \begin{minipage}[t]{0.49\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.03\columnwidth}\raggedright
8\strut
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
18\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright
3/4\strut
\end{minipage} & \begin{minipage}[t]{0.04\columnwidth}\raggedright
Mon\strut
\end{minipage} & \begin{minipage}[t]{0.49\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.03\columnwidth}\raggedright
8\strut
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
19\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright
3/6\strut
\end{minipage} & \begin{minipage}[t]{0.04\columnwidth}\raggedright
Wed\strut
\end{minipage} & \begin{minipage}[t]{0.49\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.03\columnwidth}\raggedright
8\strut
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
20\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright
3/8\strut
\end{minipage} & \begin{minipage}[t]{0.04\columnwidth}\raggedright
Fri\strut
\end{minipage} & \begin{minipage}[t]{0.49\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.03\columnwidth}\raggedright
9\strut
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
21\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright
3/11\strut
\end{minipage} & \begin{minipage}[t]{0.04\columnwidth}\raggedright
Mon\strut
\end{minipage} & \begin{minipage}[t]{0.49\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.03\columnwidth}\raggedright
9\strut
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
22\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright
3/13\strut
\end{minipage} & \begin{minipage}[t]{0.04\columnwidth}\raggedright
Wed\strut
\end{minipage} & \begin{minipage}[t]{0.49\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.03\columnwidth}\raggedright
9\strut
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
23\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright
3/15\strut
\end{minipage} & \begin{minipage}[t]{0.04\columnwidth}\raggedright
Fri\strut
\end{minipage} & \begin{minipage}[t]{0.49\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.03\columnwidth}\raggedright
10\strut
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
24\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright
3/18\strut
\end{minipage} & \begin{minipage}[t]{0.04\columnwidth}\raggedright
Mon\strut
\end{minipage} & \begin{minipage}[t]{0.49\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.03\columnwidth}\raggedright
10\strut
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
25\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright
3/20\strut
\end{minipage} & \begin{minipage}[t]{0.04\columnwidth}\raggedright
Wed\strut
\end{minipage} & \begin{minipage}[t]{0.49\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.03\columnwidth}\raggedright
10\strut
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
26\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright
3/22\strut
\end{minipage} & \begin{minipage}[t]{0.04\columnwidth}\raggedright
Fri\strut
\end{minipage} & \begin{minipage}[t]{0.49\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.03\columnwidth}\raggedright
11\strut
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
27\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright
3/25\strut
\end{minipage} & \begin{minipage}[t]{0.04\columnwidth}\raggedright
Mon\strut
\end{minipage} & \begin{minipage}[t]{0.49\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.03\columnwidth}\raggedright
11\strut
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
28\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright
3/27\strut
\end{minipage} & \begin{minipage}[t]{0.04\columnwidth}\raggedright
Wed\strut
\end{minipage} & \begin{minipage}[t]{0.49\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.03\columnwidth}\raggedright
11\strut
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
29\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright
3/29\strut
\end{minipage} & \begin{minipage}[t]{0.04\columnwidth}\raggedright
Fri\strut
\end{minipage} & \begin{minipage}[t]{0.49\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.03\columnwidth}\raggedright
12\strut
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
X\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright
4/1\strut
\end{minipage} & \begin{minipage}[t]{0.04\columnwidth}\raggedright
Mon\strut
\end{minipage} & \begin{minipage}[t]{0.49\columnwidth}\raggedright
NO CLASS (Cesar Chaves Day)\strut
\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.03\columnwidth}\raggedright
12\strut
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
30\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright
4/3\strut
\end{minipage} & \begin{minipage}[t]{0.04\columnwidth}\raggedright
Wed\strut
\end{minipage} & \begin{minipage}[t]{0.49\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.03\columnwidth}\raggedright
12\strut
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
31\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright
4/5\strut
\end{minipage} & \begin{minipage}[t]{0.04\columnwidth}\raggedright
Fri\strut
\end{minipage} & \begin{minipage}[t]{0.49\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.03\columnwidth}\raggedright
13\strut
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
32\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright
4/8\strut
\end{minipage} & \begin{minipage}[t]{0.04\columnwidth}\raggedright
Mon\strut
\end{minipage} & \begin{minipage}[t]{0.49\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.03\columnwidth}\raggedright
13\strut
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
33\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright
4/10\strut
\end{minipage} & \begin{minipage}[t]{0.04\columnwidth}\raggedright
Wed\strut
\end{minipage} & \begin{minipage}[t]{0.49\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.03\columnwidth}\raggedright
13\strut
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
34\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright
4/12\strut
\end{minipage} & \begin{minipage}[t]{0.04\columnwidth}\raggedright
Fri\strut
\end{minipage} & \begin{minipage}[t]{0.49\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.03\columnwidth}\raggedright
14\strut
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
X\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright
4/15\strut
\end{minipage} & \begin{minipage}[t]{0.04\columnwidth}\raggedright
Mon\strut
\end{minipage} & \begin{minipage}[t]{0.49\columnwidth}\raggedright
NO CLASS (Spring Break)\strut
\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.03\columnwidth}\raggedright
14\strut
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
X\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright
4/17\strut
\end{minipage} & \begin{minipage}[t]{0.04\columnwidth}\raggedright
Wed\strut
\end{minipage} & \begin{minipage}[t]{0.49\columnwidth}\raggedright
NO CLASS (Spring Break)\strut
\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.03\columnwidth}\raggedright
14\strut
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
X\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright
4/19\strut
\end{minipage} & \begin{minipage}[t]{0.04\columnwidth}\raggedright
Fri\strut
\end{minipage} & \begin{minipage}[t]{0.49\columnwidth}\raggedright
NO CLASS (Spring Break)\strut
\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.03\columnwidth}\raggedright
15\strut
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
35\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright
4/22\strut
\end{minipage} & \begin{minipage}[t]{0.04\columnwidth}\raggedright
Mon\strut
\end{minipage} & \begin{minipage}[t]{0.49\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.03\columnwidth}\raggedright
15\strut
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
36\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright
4/24\strut
\end{minipage} & \begin{minipage}[t]{0.04\columnwidth}\raggedright
Wed\strut
\end{minipage} & \begin{minipage}[t]{0.49\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.03\columnwidth}\raggedright
15\strut
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
37\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright
4/26\strut
\end{minipage} & \begin{minipage}[t]{0.04\columnwidth}\raggedright
Fri\strut
\end{minipage} & \begin{minipage}[t]{0.49\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.03\columnwidth}\raggedright
16\strut
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
38\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright
4/29\strut
\end{minipage} & \begin{minipage}[t]{0.04\columnwidth}\raggedright
Mon\strut
\end{minipage} & \begin{minipage}[t]{0.49\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.03\columnwidth}\raggedright
16\strut
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
39\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright
5/1\strut
\end{minipage} & \begin{minipage}[t]{0.04\columnwidth}\raggedright
Wed\strut
\end{minipage} & \begin{minipage}[t]{0.49\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.03\columnwidth}\raggedright
16\strut
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
40\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright
5/3\strut
\end{minipage} & \begin{minipage}[t]{0.04\columnwidth}\raggedright
Fri\strut
\end{minipage} & \begin{minipage}[t]{0.49\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.03\columnwidth}\raggedright
17\strut
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
41\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright
5/6\strut
\end{minipage} & \begin{minipage}[t]{0.04\columnwidth}\raggedright
Mon\strut
\end{minipage} & \begin{minipage}[t]{0.49\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.03\columnwidth}\raggedright
17\strut
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
42\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright
5/8\strut
\end{minipage} & \begin{minipage}[t]{0.04\columnwidth}\raggedright
Wed\strut
\end{minipage} & \begin{minipage}[t]{0.49\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.03\columnwidth}\raggedright
17\strut
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright
5/9\strut
\end{minipage} & \begin{minipage}[t]{0.04\columnwidth}\raggedright
Thu\strut
\end{minipage} & \begin{minipage}[t]{0.49\columnwidth}\raggedright
Consultation Day\strut
\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.03\columnwidth}\raggedright
17\strut
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright
5/10\strut
\end{minipage} & \begin{minipage}[t]{0.04\columnwidth}\raggedright
Fri\strut
\end{minipage} & \begin{minipage}[t]{0.49\columnwidth}\raggedright
Consultation Day\strut
\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.03\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.03\columnwidth}\raggedright
\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedright
5/15\strut
\end{minipage} & \begin{minipage}[t]{0.04\columnwidth}\raggedright
Wed\strut
\end{minipage} & \begin{minipage}[t]{0.49\columnwidth}\raggedright
08:45--10:45 AM: FINAL (ACS) EXAM\strut
\end{minipage} & \begin{minipage}[t]{0.17\columnwidth}\raggedright
\strut
\end{minipage}\tabularnewline
\bottomrule
\end{longtable}
