\hypertarget{course-information}{%
\section{Course information}\label{course-information}}

\begin{itemize}
\tightlist
\item
  \textbf{Course name and number (units)}: CHEM 128A (76409-06 LEC) (3
  Units)
\item
  \textbf{Pre-requisite}: Passed CHEM 1B/L (or CHEM 8) with grade ``C''
  or better.
\item
  \textbf{Meetings}: Mon/Wed 14:00--15:15 in Social Science Bldg Room
  204
\item
  \textbf{Instructor office}: Science 1 room 352
\item
  \textbf{Office Phone}: (559) 278-2711 (redirects to my cell phone)
\item
  \textbf{Email}: Send email through Canvas (preferred\footnote{All
    email sent through Canvas are sent to my email but sometimes I don't
    check my email for hours but do check Canvas inbox. Usually, my
    response time is \emph{within 24 hours of reading the message}. We
    also have online course tools where you can ask questions to the
    entire class at any time, making it more likely to get a quick
    response.}) or to \url{hmuchalski@mail.fresnostate.edu}
\item
  \textbf{Office Hours}: Mon/Thu 16:00--17:00
\end{itemize}

\hypertarget{hyflex-learning}{%
\subsection{HyFlex Learning}\label{hyflex-learning}}

This course is taught in a HyFlex format which combines face-to-face
(F2F) and online learning. Some students in the class will learn inside
the physical classroom and other students will connect remotely and
synchronously using Zoom when needed. Whether remote or in the
classroom, students will benefit from the same live synchronous learning
session. The goal of HyFlex is to provide a flexible and seamless
engagement for the classroom experience responsive to student needs as
well as campus, local, state, and federal guidelines. You initially
registered for this class in person and should expect to attend each
class session in the assigned classroom. If you cannot attend in person
let me know and arrange to connect via Zoom.

\newpage

\hypertarget{tldr}{%
\section{TL;DR}\label{tldr}}

\begin{itemize}
\tightlist
\item
  I want you to succeed. Your classmates want you to succeed.
\item
  Organic chemistry is a hard subject to master.
\item
  This course is designed according to \emph{flipped learning} model.
\item
  This course uses \emph{mastery grading system}. There is no
  partial/extra credit.
\item
  Official text (Klein 4 ed) is available to all students on the first
  day via Inclusive Access.
\item
  Course ends with a final exam on 12/15 at 15:30.
\item
  Don't cheat. Consequences are severe.
\end{itemize}

\hypertarget{start-here}{%
\section{Start here}\label{start-here}}

Welcome to the first semester of course in organic chemistry (CHEM
128A)! I'm Hubert Muchalski, Associate Professor in the Department of
Chemistry and Biochemistry. Before reading any further, I'd like you to
know that:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \textbf{I want you to be successful in this course.} I will do my
  utmost to help you do this, by creating and maintaining a learning
  environment based on challenge and support. ``Success'' in the course
  is more than your performance on tests. It means that you are being
  challenged to grow as a learner, that you are engaging actively with
  tasks that feed your growth, and that you are doing your best work by
  solving challenging organic chemistry problems. I also hope that you
  are here to build your lifelong learning skills so that once the
  course is over, you are better and stronger as a learner and can
  continue to learn new things independently.
\item
  \textbf{College-level organic chemistry is more than just memorizing
  structures and reactions}. You will be asked to do more than just give
  answers to problems. Your task is to seek deep understanding of
  underlying concepts and develop an array of skills such as predicting
  the outcomes of chemical reactions and properties of organic
  molecules.
\item
  \textbf{Expect to be challenged intellectually throughout this
  course.} None of these elements of success come easily. They require a
  great deal of time and attention to properly deal with ambiguity of
  the concepts and tasks in the course. This will require you to leave
  your comfort zones on a regular basis. You will need to stay engaged
  by participating in class meetings and on the class discussions.
  Students who succeed in this course have few things in common: they
  ask questions, seek understanding (not answers), form study groups,
  and help others learn.
\item
  \textbf{Intellectual struggle is normal and healthy in a challenging
  course.} You can expect at times to feel like you are really
  struggling with the material, even if learning in earlier chemistry
  courses came easy. This is a normal and healthy experience. Legitimate
  struggle is actually a sign you are doing things right---training your
  mind beyond what it is capable at the moment. My goal is to support
  you in this process.
\item
  \textbf{You have a lot of help available to you as you work.} You are
  not expected to do this all on your own. There is a lot of support to
  help you rise to the challenge. I will do my best to be available for
  consultations during office hours. You're not alone in this so please
  engage with your classmates, ask questions, seek clarification and
  provide help whenever you can.
\end{enumerate}

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

Carbon-based molecules are central to a host of chemical and biological
processes because of their broad range of function. The millions of
organic compounds alone, ranging from polymers to pharmaceuticals, make
the field important for study. Yet organic chemistry is also a highly
integrated discipline that impacts and is impacted by the other branches
of chemistry and other sciences. Indeed organic chemistry enables a
molecular understanding of physicochemical phenomena in materials
science, the environment, biology, and medicine. Because the field has
reached a high level of integration with these areas, progress in
organic chemistry continues at a fast pace and much more remains to be
discovered.

\hypertarget{course-goals-and-objectives}{%
\section{Course goals and
objectives}\label{course-goals-and-objectives}}

The goal of this course is to drive the student to appreciate the
breadth of organic chemistry by facilitating an understanding of the
principles, and the practice of applying them, to gain a working
knowledge and appreciation of organic structure and reactivity. As much
as this is true, this explanation is vague and doesn't answer a key
question: ``Why should you, the student, study organic chemistry?''

\hypertarget{why-study-organic-chemistry}{%
\subsection{Why study organic
chemistry?}\label{why-study-organic-chemistry}}

``To be an organic chemist, or course!'' one might say. The fact is,
that approximately 1\% of all students whom I taught this course are
chemists or pursue a graduate degree in organic chemistry. For most
students this course is just a part of the curriculum or a requirement
for an advanced training program in health-related field. Why, you may
wonder, is this course a hard requirement? \textbf{Successful completion
of organic chemistry is a signal to the outside world.} It demonstrates
your competence in self-regulated learning. It shows that you can
quickly learn hard abstract concepts and that you know how to work with
models and theories. Doing well in organic chemistry also reveals that
you can manage time and tasks, and that you can use highly technical
language to communicate with peers.

\hypertarget{course-learning-objectives-how}{%
\subsection{Course learning objectives
(How)}\label{course-learning-objectives-how}}

To get closer to achieving course goal, we will focus on a variety of
skills. At the successful completion of this course you will be able to:

\begin{itemize}
\tightlist
\item
  use common drawing and naming conventions to communicate the structure
  and properties of organic molecules;
\item
  analyze chemical structures and reactions to make and defend
  predictions about chemical processes;
\item
  use curved arrow notation to draw mechanisms of chemical
  transformations;
\item
  propose a synthesis of an organic molecule; and
\item
  connect the ideas of organic chemistry with your own personal and
  professional interests
\item
  ANALYZE CHOICES AT THE SYSTEM LEVEL
\end{itemize}

\hypertarget{course-content-what}{%
\subsection{Course content (What)}\label{course-content-what}}

To achieve course-level objectives we need material to work with. Topics
in this course will be focused on the principles of bonding, structure,
reactivity, and synthesis of organic molecules and materials. Lectures
and problems will often feature organic compounds and reactions in the
context of biology, pharmacy, medicine, materials, and energy science.
The second semester in the sequence also emphasizes that our only way to
molecular knowledge is through experimentation; correlating structure
with reactivity and function through wet chemical methods, spectroscopy,
and use of computational simulations.

\hypertarget{structure-of-the-course}{%
\section{Structure of the course}\label{structure-of-the-course}}

I designed this course according to the flipped learning model, an
instructional philosophy optimized for active learning. Direct
instruction is done before class meetings through structured activities
and class time is repurposed for collaborative work on creative
applications. This \href{https://vimeo.com/showcase/8484250}{video
series} highlights the basics of flipped learning.

\textbf{Before class}, your task will be to review previously covered
material, and get familiar with the basic concepts. Not all new material
needs formal instruction. Information is abundant and you can learn the
basics on your own. I will provide a list of suggested reading and video
content for you to review before the lesson.

\textbf{Class time} will be structured around agile lesson plans that
aim to operate within middle third of
\href{https://flic.kr/p/LQuqT2}{Bloom taxonomy}. There may be some small
lectures or tutorials, but active work will be the main component since
the best way to learn organic chemistry is by doing lots of problems. It
is in your best interest to come class meetings but if circumstances
arise, you will have an option to review the recorded Zoom session.

\textbf{After class} you should continue to engage with the material
through practice and deliberation on the ideas discussed in class until
you think you're ready to demonstrate your knowledge by attempting
Learning Target problems on Checkpoints.

\hypertarget{required-materials-and-technology}{%
\section{Required materials and
technology}\label{required-materials-and-technology}}

\begin{itemize}
\tightlist
\item
  \textbf{Textbook:} ``Organic Chemistry'' online textbook by David
  Klein 4th edition published by Wiley (via Immediate
  Access\footnote{This course is part of the Immediate Access program.
    All students have access to a digital version of the textbook and
    associated materials on the first day of class. Students who wish to
    purchase course materials on their own can opt-out before their
    account is automatically charged on the 10th day (5th day for Summer
    courses) of instruction. Contact the Kennel Bookstore for more
    details.}). This is 1-semester access to e-textbook and WileyPLUS
  platform. I was told by the publisher that there is an option to
  purchase paper copy in addition to e-textbook. Consider this option if
  you think you'll need access to the textbook after you're done with
  the course (MCAT/DAT prep etc.). Contact the bookstore for details.
\item
  \textbf{WileyPLUS:} Online learning platform and homework. WileyPLUS
  is integrated with Canvas and all links to assignments and materials
  will be posted on Canvas. \footnote{WileyPLUS version must be the same
    as the official edition of the textbook (4th ed.). If you opt out of
    Immediate Access and buy the textbook and access to WileyPLUS
    through other means, make sure that your access code is for the 4th
    edition of the textbook.}
\item
  \textbf{A personal computer}: running Windows or macOS, that can run
  desktop applications and has a reliable access to high-speed internet.
  A tablet device is an acceptable alternative, but the online homework
  platform is not optimized for mobile devices.
\item
  \textbf{A modern web browser}: Chrome is the recommended browser by
  Fresno State IT. Other browsers such as Edge, Firefox, or Safari are
  likely to work just as well but the support will be limited.
\item
  \textbf{Document scanning tool}: Many assignments in this course are
  designed to be prepared by hand on paper. Few people own document
  scanners nowadays, but a mobile device with a scanning app can do a
  sufficient job at converting paper documents into PDFs. There are
  number of options available for both iOS and Android. Find one that
  you like and learn how to use it.
  \url{https://fresnostate.instructure.com}.
\item
  \textbf{Zoom:} The broadcast of the class meeting will be held via
  Zoom. Links and passwords to zoom meetings will be published on
  Canvas. Make sure your Zoom client is up to date. All Zoom recordings
  will be published on Panopto.
\item
  \textbf{Active Fresno State network account} so that you can access
  email, Canvas, and Google Suite. If you have any issue with accessing
  any of the above, please let me know as soon as possible. We will use
  a variety of additional course tools during the semester, but they
  will be free to use, and you will be taught how to use them as part of
  the class.
\item
  \textbf{Student response system:} Each student will need an
  \emph{i\textgreater clicker2} remote or access to the iClicker Reef
  mobile app. The officially supported model is
  \emph{i\textgreater clicker2} (available at the Bookstore).
  \footnote{You can borrow hardware remote from a friend or buy a used
    one. Remotes need to be registered online to be linked to your name.}
\item
  \textbf{Study Guide and Solutions Manual} This is optional item that
  you can purchase for additional fee (\$15) via IA. It contains
  solutions to all problems in the textbook.
\end{itemize}

\hypertarget{types-of-graded-work}{%
\section{Types of graded work}\label{types-of-graded-work}}

You will be engaging with several kinds of activities in the course,
both to facilitate learning of the material and to demonstrate how well
you have learned it. The course uses a \emph{mastery-based grading
system} in which your work will be required to meet certain levels of
quality that demonstrate \emph{mastery}. These include:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \textbf{Learning Targets} are main skills and tasks you should be able
  to do if you're successfully learning in CHEM 128B. There are
  \textbf{16} Learning Targets in the course (see
  \protect\hyperlink{LT}{Appendix B}). Your primary goal is to provide
  evidence of mastery on as many targets as possible. You will do that
  through \emph{Checkpoints}, asynchronous at-home exams. See
  \protect\hyperlink{grading}{``How work is graded in CHEM 128A''} below
  for details.
\item
  \textbf{Application/Extension Problems (AEPs)} are challenging
  integrated homework problems where students must clearly communicate a
  complete solution. AEPs measure student skills across multiple
  learning objectives, will require a formal writeup, and may require
  additional technology. Submission and grading of AEPs is discussed in
  \protect\hyperlink{grading}{``How work is graded in CHEM 128A''}
  section below.
\item
  \textbf{Class Preps} are short quizzes on WileyPLUS to get a sense of
  how much you learned on your own from reading and watching videos.
  Additional purpose of this assignment is to provide me with
  information about issues that the class is having, prior to class
  meetings. You get credit for the Prep assignment if you complete it
  before the deadline and if each item has a response that represents a
  good faith effort to be right. Remember, \emph{mistakes are not
  penalized}.
\item
  \textbf{Participation} Taking part in student response polls in class
  (iClicker). You will receive one participation credit if you answer
  75\% of questions in class session. Correctness is not factored into
  the score, only participation.
\item
  \textbf{Online Homework (WileyPLUS)} will help you identify knowledge
  gaps in each chapter. This is an adaptive assignment which means that
  the set of questions is tailored to your knowledge. The number of
  questions in the set varies depending how well you know the material.
  As your answer questions, the progress bar tracks completion. It can
  increase and decrease based on how you're doing and you earn points
  for reaching benchmarks on the Progress bar. You'll keep your points
  even if your Progress decreases. Work toward 100\% Progress to
  complete your assignment and show that you know your stuff.
\item
  \textbf{Final exam} will be on \textbf{Wednesday, December 15th, 2021
  at 15:30}. \sout{The final exam is composed of 70 multiple choice
  questions designed by experts from the American Chemical Society. Exam
  time is 110 minutes.} Final exam time block will be the last
  opportunity to reassess learning targets. This is the only Checkpoint
  that will be synchronous for all students, lasting 2 hours and without
  an option of time window extension.
\end{enumerate}

\hypertarget{grading}{%
\subsection{How student work is graded}\label{grading}}

\hypertarget{checkpoints}{%
\subsubsection{Checkpoints}\label{checkpoints}}

One of your primary responsibilities in the course is to demonstrate as
much skill as possible on as many Learning Targets as possible through
doing ``acceptable'' work on \emph{Checkpoints}. Checkpoints are timed
do-at-home exams offered every 10--14 days (see schedule at the end of
syllabus). You will have a 24-hour window of time during which a packet
of problems will be available on Canvas for download. You will have 2
hours, from the moment you download the document, to submit your work.
Checkpoints contain one problem (often with multiple parts) per Learning
Target. Each problem is graded separately and has its own criteria for
acceptable work.

Your skill on is indicated in the gradebook separately for each Learning
Target using a 3-level rubric:

\begin{itemize}
\tightlist
\item
  \textbf{No Rating} indicates that that you did not attempt the
  learning target or the attempt was unsuccessful. Everyone begins the
  semester with ``No Rating'' on all Learning Targets.
\item
  \textbf{Proficiency} indicates you completed \textbf{one} Checkpoint
  problem on a Learning Target and the solution met the standards for
  acceptable work.
\item
  \textbf{Mastery} indicates you completed \textbf{a second} Checkpoint
  problem on a Learning Target and the solution met the standards for
  acceptable work.
\end{itemize}

\textbf{Every Checkpoint is cumulative}, with new Learning Targets
represented but also new versions of older ones. This will allow you to
reattempt, on a limited basis, any Learning Target you haven't mastered.

\hypertarget{aeps}{%
\subsubsection{AEPs}\label{aeps}}

AEP assignments are like homework, they are not timed but they have
deadlines (4 weeks from when they become available). Your work on
Application/Extension Problems (AEPs) is scored similarly to Learning
Target problems (pass/no pass) and can be revised and resubmitted (with
some limitations described below).

\hypertarget{revisions}{%
\subsection{Revisions and reassessment}\label{revisions}}

You can reattempt Learning Target problems which you did not master yet
at a later \emph{Checkpoint}. AEPs can be revised and resubmitted at any
time before the deadline and they will be regraded using the same
standards as originally used. \emph{Only one AEP submission can may be
made per week}. This can be one new submission, or one revision. A
second submission can be purchased with a
\protect\hyperlink{tokens}{token} (below) but three or more submissions
in a week are not allowed under any circumstance.

\hypertarget{tokens}{%
\subsection{Tokens}\label{tokens}}

Every student starts with five tokens, a fake currency which can be
spent to purchase exceptions to course policies: a) submission of second
AEP (either revision or new submission) in a given week; or 1-hour
extension of checkpoint upload time window. Tokens may not be
``stacked''. For example, you cannot spend 3 tokens to get a 3-hour
extension on \emph{Checkpoint} submission deadline.

\hypertarget{final-letter-grade}{%
\section{Final letter grade}\label{final-letter-grade}}

The mastery-based grading system insists that you show consistent
excellence in all assignments in the course. Your course grade is
determined using the table below. In order to earn a particular letter
grade, each requirement must be met in the column for that grade,
meaning you will earn \textbf{the highest grade for which \emph{all} the
requirements are met}. Numerical values in the table indicate the
minimum level needed to meet the requirement; amounts above this level
also meet the requirement.

\begin{longtable}[]{@{}lllll@{}}
\toprule
Category & D & C & B & A \\
\midrule
\endhead
LTs Mastered & 5 & 8 & 11 & 14 \\
AEP passed & & 1 & 4 & 7 \\
Class Preps & 5 & 10 & 15 & 20 \\
iClicker Credits & 5 & 10 & 15 & 20 \\
WileyPLUS Homework & 70 & 80 & 90 & 100 \\
\bottomrule
\end{longtable}

There are no statistical or numerical adjustments (a.k.a. grading on a
curve). Outstanding work in one category, on AEPs for example, does not
compensate for poor work in another category. Failing grade (F) is given
if not all the requirements for a ``D'' are met.

Read the example on the next page and referring back to the table above
try to determine the final letter grade.

\hypertarget{example}{%
\subsubsection{Example}\label{example}}

At the end of the semester Morgan showed mastery on 13 LTs, passed 9
AEPs, did all Class Preps, collected 25 iClicker credits, and 120 points
on Homework.\footnote{Morgan will receive ``B'' in the course, because
  Morgan did not meet all requirements for A (minimum 14 LTs mastered).
  Exceeding requirements in other categories is irrelevant.}

\hypertarget{course-policies}{%
\section{Course policies}\label{course-policies}}

\hypertarget{technology-issues-when-submitting-work}{%
\subsection{Technology issues when submitting
work}\label{technology-issues-when-submitting-work}}

It is the student's responsibility to make sure these items are
submitted on time, even if technology issues arise. Technology issues
that are avoidable or resolved with a simple work-around will not be
considered valid grounds for a deadline extension. For example, if you
are trying to upload a Lab to Canvas and Canvas won't accept the file,
you should try again later, use different browser, upload to Google
Drive and share a private link or send the file as an email attachment
until you can upload it successfully.

\hypertarget{academic-integrity}{%
\subsection{Academic integrity}\label{academic-integrity}}

Academic dishonesty carries with it strong punitive measures mandated by
Fresno State policies, including possible automatic failure of the
course or suspension from the university. Details are described in
Academic Policy Manual 235 which you can read here:
\url{http://www.fresnostate.edu/aps/documents/apm/235.pdf}.
\textbf{Every student has the responsibility of reading and
understanding these policies, especially the consequences for engaging
in academically dishonest activities.}

Some of the work you will do in the course involves collaboration; at
other times collaboration may be allowed but not required; while at
others it may not be allowed. Here are the rules for collaboration on
each kind of work you do:

\begin{itemize}
\tightlist
\item
  \emph{Class Prep}, \emph{WileyPLUS Homework}: You may collaborate with
  others, but your writeup must be your own. You may not copy someone's
  work and submit it as your own, nor may you copy the ideas from
  someone and simply change how it's presented (or change wording).
\item
  \emph{Checkpoints}, \emph{AEPs}: No interactions at all with another
  person or with unauthorized sources on the internet is allowed. Any
  evidence of using information from another person or source will be
  investigated as academic dishonesty.
\end{itemize}

\hypertarget{resources-you-can-and-cannot-use-when-submitting-graded-work}{%
\subsubsection{Resources you can and cannot use when submitting graded
work}\label{resources-you-can-and-cannot-use-when-submitting-graded-work}}

Here are the approved resources you can access on all \emph{Checkpoints}
and \emph{AEPs}:

\begin{itemize}
\tightlist
\item
  the textbook;
\item
  video or document posted on Canvas site for this courses (but not
  other courses);
\item
  slides, class meeting notes, and other materials generated during
  class time; and
\item
  class zoom recordings.
\end{itemize}

\textbf{Any resource NOT included on this list is to be considered
off-limits and not approved for use on Checkpoints. Evidence of using
unapproved resources will be considered academic dishonesty.} This
includes:

\begin{itemize}
\tightlist
\item
  solution websites such as Chegg;
\item
  other students in the class, or past students from other CHEM 128
  classes; and
\item
  other textbooks or videos not included above.
\end{itemize}

All suspected instances of academic dishonesty will be thoroughly
investigated, and whether a student has committed academic dishonesty is
my determination to make based on the evidence. If I determine academic
dishonesty has been committed, a report will be filed with the Dean of
Students office, and the minimum penalty will be:

\begin{itemize}
\tightlist
\item
  ``no pass'' grade on a checkpoint and no possibility for retake;
\item
  ``no pass'' on AEP assignment and no possibility for revision; and
\item
  point deduction on final ACS exam.
\end{itemize}

\hypertarget{deadlines-and-late-work}{%
\subsection{Deadlines and late work}\label{deadlines-and-late-work}}

Deadlines for course work are clearly indicated on the Course Calendar;
in cases of apparent conflict between dates, always assume that the
Course Calendar is right.

\begin{itemize}
\tightlist
\item
  \emph{Class Prep} and \emph{WileyPLUS Homework}: No extensions to
  deadlines are available. Simply submit a good faith effort on all
  items by the deadline.
\item
  \emph{Checkpoints}: Submission window may be extended by spending a
  token. No other extensions are available.
\item
  \emph{AEPs} will be active for submission for (re)assessment for 4
  weeks. You simply submit your work when it is ready to be graded
  (subject to weekly limits). This deadline will not be extended.
\end{itemize}

\hypertarget{intellectual-property}{%
\subsection{Intellectual Property}\label{intellectual-property}}

As part of your participation in virtual/online instruction, please
remember that the same student conduct rules that are used for in-person
classrooms instruction also apply for virtual/online classrooms.
Students are prohibited from any unauthorized recording, dissemination,
or publication of any academic presentation, including any online
classroom instruction, for any commercial purpose. In addition, students
may not record or use virtual/online instruction in any manner that
would violate copyright law. Students are to use all online/virtual
instruction exclusively for the educational purpose of the online class
in which the instruction is being provided. Students may not re-record
any online recordings or post any online recordings on any other format
(e.g., electronic, video, social media, audio recording, web page,
internet, hard paper copy, etc.) for any purpose without the explicit
written permission of the faculty member providing the instruction.
Exceptions for disability-related accommodations will be addressed by
Services for Students with Disabilities (SSD) working in conjunction
with the student and faculty member.

\hypertarget{dropping-the-course}{%
\subsection{Dropping the course}\label{dropping-the-course}}

Dates and details on withdrawing from courses are described on the
\href{http://fresnostate.edu/studentaffairs/are/registration/add-drop-deadlines.html}{Admissions
web pages}.

A \emph{serious and compelling reason} is defined as an unexpected
condition that is not present prior to enrollment in the course that
unexpectedly arises and interferes with a student's ability to attend
class meetings and/or complete course requirements. The reason must be
acceptable to and verified by the instructor of record and the
department chair. The condition must be stated in writing on the
appropriate form. The student must provide documentation that
substantiates the condition. Failing or performing poorly in a class is
not an acceptable ``serious and compelling reason'' within the
University policy, nor is dissatisfaction with the subject matter, class
or instructor.

\hypertarget{changes-to-this-syllabus}{%
\subsection{Changes to this syllabus}\label{changes-to-this-syllabus}}

Changes to this syllabus may occur during the term. In those cases, the
changes will be announced in class and online, and if appropriate,
students will be given a voice on how the changes will be implemented.
It is your responsibility stay current on the information passed along
in course announcements and any changes that take place.

\hypertarget{credits}{%
\subsection{Credits}\label{credits}}

Large portions of the language of this syllabus as well as ideas related
to mastery grading and flipped learning were adapted from the syllabi of
\href{https://hackmd.io/@rtalbert235}{Prof.~Robert Talbert} (Grand
Valley University).

\hypertarget{university-policies-and-disclaimers}{%
\section{University policies and
disclaimers}\label{university-policies-and-disclaimers}}

In addition to course policies, you are expected to be familiar with
Academic Regulations described in the
\href{http://www.fresnostate.edu/catalog/academic-regulations/}{University
Catalog} as well as policies listed below.

\textbf{Students with Disabilities}: Upon identifying themselves to the
instructor and the university, students with disabilities will receive
reasonable accommodation for learning and evaluation. For more
information, contact Services to Students with Disabilities in the Henry
Madden Library, Room 1202 (278-2811).

\begin{itemize}
\tightlist
\item
  Class Schedule Policies:
  \url{http://fresnostate.edu/studentaffairs/classschedule/policy/}
\item
  Copyright Policy: \url{http://libguides.csufresno.edu/copyright}
\item
  Students with Disabilities:
  \url{http://fresnostate.edu/studentaffairs/careers/students/interests/disabilities.html}
\item
  Academic Integrity and Honor Code:
  \url{http://www.fresnostate.edu/academics/facultyaffairs/documents/apm/236.pdf}
\item
  Policy on Cheating and Plagiarism:
  \url{http://fresnostate.edu/studentaffairs/studentconduct/policies/cheating-plagiarism.html}
\item
  Add/Drop Course:
  \url{http://www.fresnostate.edu/studentaffairs/registrar/registration/}
\item
  Computer requirements:
  \url{https://www.fresnostate.edu/catalog/academic-regulations/index.html\#computerreq}
\item
  Disruptive classroom behavior:
  \url{http://www.fresnostate.edu/academics/facultyaffairs/documents/apm/419.pdf}
\end{itemize}

\hypertarget{university-services}{%
\section{University Services}\label{university-services}}

\begin{itemize}
\tightlist
\item
  \href{http://fresnostateasi.org/}{Associated Students, Inc.}
\item
  \href{http://fresnostate.edu/studentaffairs/dsc/index.html}{Dream
  Success Center}
\item
  \href{http://fresnostate.edu/studentaffairs/lrc}{Learning Center
  Information}
\item
  \href{https://www.fresnostate.edu/studentaffairs/health/}{Student
  Health and Counseling Center}
\item
  \href{http://www.fresnostate.edu/artshum/writingcenter/}{Writing
  Center}
\end{itemize}

\newpage

\hypertarget{checkpoint-schedule}{%
\section{Appendix A: Schedule of
Checkpoints}\label{checkpoint-schedule}}

\begin{longtable}[]{@{}llll@{}}
\toprule
Day & Date & Checkpoints & LTs active \\
\midrule
\endhead
Thu & Aug-26 & Checkpoint ZERO & \\
Thu & Sep-02 & Checkpoint 1 & 1,2 \\
Thu & Sep-09 & Checkpoint 2 & 1--3 \\
Thu & Sep-23 & Checkpoint 3 & 1--7 \\
Thu & Oct-07 & Checkpoint 4 & 1--10 \\
Thu & Nov-04 & Checkpoint 5 & 3--12 \\
Wed & Nov-10 & Checkpoint 6 & 4--12 \\
Thu & Nov-18 & Checkpoint 7 & 4--16 \\
Thu & Dec-02 & Checkpoint 8 & 8--16 \\
Thu & Dec-09 & Checkpoint 9 & 1--16 \\
Wed & Dec-15 & Checkpoint Encore & 1--16 \\
\bottomrule
\end{longtable}

\hypertarget{LT}{%
\section{Appendix B: Learning Targets}\label{LT}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  I can read molecular representations and deduce bonding information
  (hybridization, formal charge, geometry, valence, polarization).
\item
  I can identify functional groups and convert between different drawing
  conventions.
\item
  I can distinguish between localized and delocalized bonding. I can
  draw resonance structures to show electron delocalization and assess
  relative their relative contribution to the electronic character of
  the molecule.
\item
  I can use the Brønsted--Lowry theory to explain pKa trends of organic
  acids and correlations between structure and thermodynamic stability
  of organic bases.
\item
  I can use conformational analysis to assess relative energy of
  conformations
\item
  I can identify chirality centers in molecules. I can assign absolute
  and relative labels to designate configurational isomerism
  (Cahn--Ingold--Prelog, cis/trans, E/Z, etc.).
\item
  I can use IUPAC nomenclature rules to convert structure to name and
  name to structure.
\item
  I can identify types of (stereo)isomeric relationships between
  molecules. I can use projections to demonstrate stereoisomeric
  relationships.
\item
  I can categorize chemical transformations as substitution, addition,
  or elimination. I can identify reaction steps, draw curved arrow
  mechanisms, and identify flaws in mechanisms.
\item
  I can analyze thermodynamics and kinetics of chemical reactions and
  use reaction--energy diagrams to communicate reaction profiles.
\item
  I can solve synthetic problems involving alkyl halides and sulfonates:
  substitution and elimination reactions.
\item
  I can use conformational analysis to make predictions about
  selectivity of elimination reactions.
\item
  I can solve synthetic problems involving alkenes
\item
  I can use explain selectivity and divergent reaction pathways of
  nucleophilic substitution, β-elimination, and addition reactions.
\item
  I can solve synthetic problems involving alkynes
\item
  I can solve synthetic problems involving alcohols
\end{enumerate}
